### 2016-04-23 writing/latex/coincidence.tex
Getting closer

\chapter{Coincidences amongst families of mesh patterns and classical patterns}\label{chap:coincs}
One interesting question to ask about permutation patterns considers when a
pattern may be avoided by, or contained in, arbitrary permutations. Two
patterns \(\pi\) and \(\sigma\) are said to be \emph{coincident} if the set
of permutations that avoid \(\pi\) is the same as the set of permutations that
avoid \(\sigma\). This extends to sets of patterns as well as single patterns.

@@

>>>>

\chapter[Coincidence Classification]{Coincidences amongst families of mesh patterns and classical patterns}\label{chap:coincs}
One interesting question to ask about permutation patterns considers when a
pattern may be avoided by, or contained in, arbitrary permutations. Two
patterns \(\pi\) and \(\sigma\) are said to be \emph{coincident} if the set
of permutations that avoid \(\pi\) is the same as the set of permutations that
avoid \(\sigma\). This extends to sets of patterns as well as single patterns.

@@

By discussion of a number of rules we will show that the number of coincidence
classes follows the values shown in  \TableRef{tab:domclasses}.

\begin{table}[htb]
\begin{center}
\begin{tabularx}{\textwidth}{c|Y|Y|Y|Y|}
\cline{2-5}
& \multicolumn{4}{|c|}{Dominating Pattern}\\
\cline{2-5}
& \multicolumn{2}{|c|}{\(\perm{2,3,1}\)}&\multicolumn{2}{|c|}{\(\perm{3,2,1}\)}\\
\cline{2-5}
& \(\perm{1,2}\)&\(\perm{2,1}\)&\(\perm{1,2}\)&\(\perm{2,1}\)\\
\hline
\multicolumn{1}{|r|}{No Dominating rule}&\(220\)&\(220\)&\(220\)&\(220\)\\
\hline
\multicolumn{1}{|r|}{First Dominating rule}&\(85\)&\(43\)&\(220\)&\(29\)\\
\hline
\multicolumn{1}{|r|}{Second Dominating rule}&\(59\)&\(39\)&\(220\)&\(29\)\\
\hline
\multicolumn{1}{|r|}{Third Dominating rule}&\(56\)&\(39\)&\(220\)&\(29\)\\
\hline
\multicolumn{1}{|r|}{Experimental class size}&\(56\)&\(39\)&\(213\)&\(29\)\\
\hline
\end{tabularx}
\end{center}
    \caption{Class number reduction by application of Dominating Rules}
    \label{tab:domclasses}
\end{table}

### 2016-04-23 writing/latex/confut.tex
Getting closer

\chapter{Conclusions and Future work}
From \ChapterRef{chap:coincs} it is can be seen that automatically classifying
coincidences of mesh patterns is a difficult task, establishing rules for longer
dominating patterns requires many more cases to be taken.

>>>>

\chapter{Conclusions and Future work}
From \ChapterRef{chap:coincs} it is can be seen that automatically classifying
coincidences of mesh patterns is a difficult task, establishing rules for longer
dominating patterns requires many more cases to be taken. It would however
be interesting to consider the self application of the Dominating Rules to mesh
patterns in order to try to capture some of the coincidences described in
\textcite{DBLP:journals/combinatorics/HilmarssonJSVU15} and \textcite{journals/combinatorics/BrandenC11}.

It is also possible to take sets of mesh patterns instead of a single mesh pattern
when considering dominating rules, and expressing coincidence between these sets.
Doing this may give nice enumerative results.

It would be interesting to consider a systematic explanation of Wilf-equivalences
amongst classes where \(\perm{3,2,1}\) is the dominating pattern using the
construction presented in \cite[Sec.~12]{2015arXiv151203226B}, in order to directly
reach enumeration and hopefully establish some of the non-trivial Wilf-equivalences
between classes with different dominating patterns.

### 2016-04-23 writing/latex/introduction.tex
Getting closer

\section{Mesh Patterns}
Mesh Patterns were introduced by Brändén and Claesson\cite{journals/combinatorics/BrandenC11} to capture explicit expansions
for certain permutation statistics. They are a natural extension of Classical
permutation patterns. A \emph{mesh-pattern} is a pair
\begin{equation*}
    p = (\tau,R)\text{ with } \tau \in \mathfrak{S}_k \text{ and } R \subseteq
    [0,k]\times [0,k].
\end{equation*}
By this definition the empty permutation \(\varepsilon\) as a mesh pattern consisting solely of the
box \((0,0)\).

@@

>>>>

Knuth's statements were exercises in showing that the permutations avoiding the
pattern \(\perm{2,3,1}\) completely categorise permutations that are sortable to
the identity permutation using only a single stack, and that permutations avoiding the
pattern \(\perm{3,2,1}\) completely categorise permutations that are sortable to
the identity permutation using only a single queue with bypass.

\section{Mesh Patterns}
Mesh Patterns were introduced by \textcite{journals/combinatorics/BrandenC11} to capture explicit expansions
for certain permutation statistics. They are a natural extension of Classical
permutation patterns. A \emph{mesh-pattern} is a pair
\begin{equation*}
    p = (\tau,R)\text{ with } \tau \in \mathfrak{S}_k \text{ and } R \subseteq
    [0,k]\times [0,k].
\end{equation*}
By this definition the empty permutation \(\varepsilon\) as a mesh pattern consisting solely of the
box \((0,0)\).

@@

In the past people have studied different classes
of permutations that can be described by mesh patterns. \textcite{babstein2000}
considered \emph{vincular} patterns (also known as \emph{generalised} or \emph{dashed} patterns),
those where two adjacent entries in the pattern must be adjacent in the permutation,
\ie entire columns are shaded in the mesh.
\textcite{MR2652101} look at classes of pattern where both columns and rows
can be shaded, these are called \emph{bivincular} patterns.
\emph{Bruhat-restricted} patterns were studied by \textcite{MR2264071} in order
to establish necessary conditions for a Schubert variety to be Gorenstein.
Mesh patterns also encompass a subset of \emph{barred} patterns introduced by
\textcite{MR2716312}.

Avoiding pairs of patterns of the same length with certain properties has
also been studied in the past, \textcite{MR2178749} considered avoiding a
pair of vincular patterns of length 3. \textcite{2015arXiv151203226B} study avoiding
a vincular and a covincular pattern simultaneously in order to achieve some
interesting counting results. However, very little work has been done on avoiding
a mesh pattern and a classical pattern simultaneously, in this work we aim to
establish some ground in this field by computing coincidences and Wilf-classes
and calculating some of the enumerations of avoiders of a mesh pattern of length
2 and a classical pattern of length 3.
